Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-14 prop_letter.tex
small things

\begin{thm}\label{thm:Shapley}
  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
  of events~$\events'\subseteq\events$ commutes, then
  $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
\end{thm}

>>>>

\begin{thm}\label{thm:Shapley}
  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
  of events~$\events_C\subseteq\events$ commutes, then
  $\coreBorn\left(\bar{\mu},\events_C\right)\ne\emptyset$.
\end{thm}
